Environments and eval in R

### 2021-04-16 analysis/environments.Rmd
Enclos class added for synthetic environments

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    type = expr_resolved_type_tag, #   Argument type
    ev_call = eval_call_expression,
    ev_expr = expr_expression,
    n_op = interp_eval,
    hash = expr_resolved_hash,
    envir = envir_expression,
    envir_type,
    caller_expression,
    environment_class,
    enclos = enclos_expression
  ) -> E_envir

@@

```{r envir_list}
eval_calls_env_list <- eval_calls_explicit %>% filter(envir_type == "list")

@@

And with the higher-level categories:

```{r}
high_level_new <- env_calls %>% filter(!is.na(new_env)) %>% 
  mutate(category = case_when(
    !is.na(hierarchy) ~ "function", # Will also include _callee
    specific_env == "global" ~ "global",
    specific_env == "empty" ~ "empty",
    str_detect(specific_env, fixed("loop")) ~ "function", #if it is loop, it means that we found the eval env in the frames,
    !is.na(specific_env) ~ "package"
  ))

high_level_new_sites <- high_level_new %>%group_by(category) %>%
  summarise(n = n_distinct(src_ref)) %>% 
  arrange(desc(n)) %>% 
  mutate(pc = ratio(n, nb_new_env_sites), cpc = cumsum(pc))

@@

synthetic_envs <- env_classes %>% filter(envir_type %in% c("list", "NULL", "pairlist") | !is.na(new_env) | specific_env == "empty")
nb_synthetic_sites <- n_distinct(synthetic_envs$src_ref)

>>>>

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    type = expr_resolved_type_tag, #   Argument type
    ev_call = eval_call_expression,
    ev_expr = expr_expression,
    n_op = interp_eval,
    hash = expr_resolved_hash,
    envir = envir_expression,
    envir_type,
    caller_expression,
    environment_class,
    enclos = enclos_expression,
    enclosure_class,
    enclos_type
  ) -> E_envir

@@

```{r envir_list}
eval_calls_env_list <- eval_calls_explicit %>% filter(envir_type %in% c("list", "pairlist"))

@@

## Synthetic

This corresponds to `new` and to `list/NULL/pairlist`:

```{r}
list_like_envs <- E_envir %>% filter(envir_type %in% c("pairlist", "list", "NULL")) %>% 
  extract(enclosure_class, regex = "((?:new\\+)*)(?:caller-(-?[[:digit:]]+)-)?(.*)", into = c("new_env", "hierarchy", "specific_env"), remove = FALSE, convert = TRUE) %>%
    mutate(specific_env = na_if(specific_env, ""), new_env = str_count(new_env, fixed("new+"))) 
  # We keep new.env not NA because it is used for the classification of new envs...

other_synth_envs <- env_classes %>% filter(!is.na(new_env) | specific_env == "empty")

synthetic_envs <- bind_rows(list_like_envs, other_synth_envs)
nb_synthetic_sites <- n_distinct(synthetic_envs$src_ref)
```

```{r}
high_level_new <- synthetic_envs %>% 
  mutate(category = case_when(
    !is.na(hierarchy) ~ "function", # Will also include _callee
    specific_env == "global" ~ "global",
    specific_env == "empty" | enclos_type == "NULL" ~ "empty",
    str_detect(specific_env, fixed("loop")) ~ "function", #if it is loop, it means that we found the eval env in the frames,
    !is.na(specific_env) ~ "package"
  ))

high_level_new_sites <- high_level_new %>%group_by(category) %>%
  summarise(n = n_distinct(src_ref)) %>% 
  arrange(desc(n)) %>% 
  mutate(pc = ratio(n, nb_synthetic_sites), cpc = cumsum(pc))

@@
